---
title: "INTERACT_Vic_Health_Comparison"
author: "Jonathan Slaney"
date: "12/02/2020"
output: html_document
---

```{r setup, message=FALSE,warning=FALSE, include=FALSE, results='asis'}

knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE)

# Pre Process Your Data
# Add applicable packages to the R Markdown
library(knitr)
library(kableExtra)
library(plyr)
library(survey)
library(ggplot2)
library(reshape2)
library(RColorBrewer)
library(dplyr)
library(tidyr)
library(kableExtra)
library(gridExtra)
library(forcats)
library(sjmisc)
library(lubridate)
library(eeptools)
library(likert)
library(data.table)
library(stringr)

# Set Working Directory 
#setwd("Volumes/hkr-storage/Research/dfuller/Walkabilly/studies/INTERACT/Data/Victoria/Survey Data/")
w2new <- read.csv("health_2vicnew_main_bfd440e.csv")
w2ret <- read.csv("health_2vic_main_bfd440e.csv")
w1 <- read.csv("health_1vic_main_bfd440e.csv")
#add wav

d <- bind_rows(w2new, w2ret, w1)

cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7") #COLOURBLIND PALETTE 
INTERACTPalette <- c("#1596FF", "#76D24A", "#404041", "#666666", "#EBF0F8") #ALLBRANDING 
INTERACTPalettecont <- c("#76D24A", "#6BCB5E", "#60C472", "#55BE86", "#4AB79A", "#40B0AE", "#35AAC2", "#2AA3D6", "#1F9CEA", "#1596FF") #10 
INTERACTPaletteSet <- c("#76D24A", "#1596FF", "#291EF8" ,"#FFD21F", "#EB2EBA","#EBF0F8", "#FF6A6A", "#AC26F2", "#1596FF", "#E5364D") #10
INTERACTPalette3 <- c("#76D24A", "#60C472", "#4AB79A",  "#35AAC2", "#1F9CEA", "#1596FF") #6
INTERACTPaletteYN <- c("#1596FF", "#404041", "#EBF0F8") #3
INTERACTfade <- c("#1596FF", "#2ca0ff", "#43abff", "#5bb5ff", "#72c0ff", "#8acaff", "#a1d5ff", "#b8dfff", "#d0eaff", "#e7f4ff", "#f3f9ff", "#ffffff") #12
INTERACTshortfade <- c("#1596FF", "#43abff", "#72c0ff",  "#a1d5ff",  "#d0eaff", "#ffffff") #6 
INTERACTshorterfade <- c("#1596FF", "#72c0ff","#d0eaff", "#ffffff") #4

```

# Wave 1 and Wave 2 Comparisons

## *Section 1: Transportation*

## Q1: How many bicycles are kept in your household?{.tabset}

### Adult bikes
```{r, echo=FALSE}

##### Setup variable name

var_name <- d$transp_bikes_adults

##### Table

t_1 <- d %>%
          group_by(wave_id) %>%
            summarise(n = n(),
                      mean = mean(var_name, na.rm = TRUE),
                      median = median(var_name, na.rm = TRUE),
                      sd = sd(var_name, na.rm = TRUE)) 

kable(t_1)  %>%   kable_styling(bootstrap_options = "striped", full_width = T, position = "left")

##### Figure

ab <- ggplot(d, aes(x = var_name)) + 
  geom_histogram(binwidth = 1, fill="#76D24A", na.rm = TRUE) + 
  xlab("Number of bicycles for adults") 

ab + facet_wrap(vars(wave_id))
```

### Children bikes

```{r, echo=FALSE}
var_name <- d$transp_bikes_kids

t_1 <- d %>%
          group_by(wave_id) %>%
            summarise(n = n(),
                      mean = mean(var_name, na.rm = TRUE),
                      median = median(var_name, na.rm = TRUE),
                      sd = sd(var_name, na.rm = TRUE)) 

kable(t_1)  %>%   kable_styling(bootstrap_options = "striped", full_width = T, position = "left")

cb <- ggplot(d, aes(x = var_name)) + 
  geom_bar(fill="#76D24A", na.rm = TRUE) + xlab("Number of bicycles for children") + 
  scale_x_continuous()
cb + facet_wrap(vars(wave_id))  
```

## Q2: On a scale of 1 to 5, with 1 being 'very safe' and 5 being 'very dangerous', overall, how safe do you think cycling is in your city? 
```{r, echo=FALSE}

##### Setup variable name

var_name <- d$bike_safety

# plot bike_safety with group_by(wave_id, bike_safety_f)
d$var_name_f <- revalue(as.factor(var_name), c("1" = "Very safe", "2" = "Somewhat safe", "3" = "Neither safe nor unsafe", "4" = "Somewhat dangerous", "5" = "Very dangerous"))

var_name_f <- d$var_name_f

##### Table

t_1 <- d %>%
          group_by(wave_id, var_name_f) %>%
            summarise(n = n()) %>%
            mutate(pct = n / sum(n))

kable(t_1)  %>%   kable_styling(bootstrap_options = "striped", full_width = T, position = "left")

##### Figure

p <- ggplot(d, aes(var_name_f,  fill = var_name_f)) + theme(axis.text.x = element_text(angle=90, vjust = .6)) + 
  geom_bar() +
  scale_fill_manual(values = INTERACTPalette3) +
  guides(fill=FALSE) +
      ylab("Count") +
      xlab("Perception of bicycle risk") +
      ggtitle("Overall, how safe do you think cycling is in your city?") + 
  facet_wrap(~ wave_id)
plot(p)
```

## Q3: How often do you typically travel by bicycle during each season?{.tabset}

### Fall

```{r, echo=FALSE}
var_name <- d$bike_freq_a

t_1 <- d %>%
          group_by(wave_id) %>%
            summarise(n = n(),
                      mean = mean(var_name, na.rm = TRUE),
                      median = median(var_name, na.rm = TRUE),
                      sd = sd(var_name, na.rm = TRUE)) 

kable(t_1)  %>%   kable_styling(bootstrap_options = "striped", full_width = T, position = "left")

p2 <- ggplot(d, aes(var_name)) + 
  theme(axis.text.x = element_text(angle=90, vjust = .6)) + 
  geom_histogram(fill="#76D24A") +
  scale_fill_manual() +
  guides(fill=FALSE) +
      ylab("Count") +
      xlab("Bicycling number of days in fall") +
      ggtitle("How often do you typically travel by bicycle during the fall?") + 
  facet_wrap(~ wave_id)
plot(p2)
```

### Winter

```{r, echo=FALSE}
var_name <- d$bike_freq_b

t_1 <- d %>%
          group_by(wave_id) %>%
            summarise(n = n(),
                      mean = mean(var_name, na.rm = TRUE),
                      median = median(var_name, na.rm = TRUE),
                      sd = sd(var_name, na.rm = TRUE)) 

kable(t_1)  %>%   kable_styling(bootstrap_options = "striped", full_width = T, position = "left")

p2 <- ggplot(d, aes(var_name)) + 
  theme(axis.text.x = element_text(angle=90, vjust = .6)) + 
  geom_histogram(fill="#76D24A") +
  scale_fill_manual() +
  guides(fill=FALSE) +
      ylab("Count") +
      xlab("Bicycling number of days in winter") +
      ggtitle("How often do you typically travel by bicycle during the winter?") + 
  facet_wrap(~ wave_id)
plot(p2)
```

### Spring

```{r, echo=FALSE}
var_name <- d$bike_freq_c

t_1 <- d %>%
          group_by(wave_id) %>%
            summarise(n = n(),
                      mean = mean(var_name, na.rm = TRUE),
                      median = median(var_name, na.rm = TRUE),
                      sd = sd(var_name, na.rm = TRUE)) 

kable(t_1)  %>%   kable_styling(bootstrap_options = "striped", full_width = T, position = "left")

p2 <- ggplot(d, aes(var_name)) + 
  theme(axis.text.x = element_text(angle=90, vjust = .6)) + 
  geom_histogram(fill="#76D24A") +
  scale_fill_manual() +
  guides(fill=FALSE) +
      ylab("Count") +
      xlab("Bicycling number of days in spring") +
      ggtitle("How often do you typically travel by bicycle during the spring?") + 
  facet_wrap(~ wave_id)
plot(p2)
```

### Summer

```{r, echo=FALSE}
var_name <- d$bike_freq_d

t_1 <- d %>%
          group_by(wave_id) %>%
            summarise(n = n(),
                      mean = mean(var_name, na.rm = TRUE),
                      median = median(var_name, na.rm = TRUE),
                      sd = sd(var_name, na.rm = TRUE)) 

kable(t_1)  %>%   kable_styling(bootstrap_options = "striped", full_width = T, position = "left")

p2 <- ggplot(d, aes(var_name)) + 
  theme(axis.text.x = element_text(angle=90, vjust = .6)) + 
  geom_histogram(fill="#76D24A") +
  scale_fill_manual() +
  guides(fill=FALSE) +
      ylab("Count") +
      xlab("Bicycling number of days in summer") +
      ggtitle("How often do you typically travel by bicycle during the summer?") + 
  facet_wrap(~ wave_id)
plot(p2)
```

## Q4: How often are your cycling trips made with children?

```{r, echo=FALSE}
##### Setup variable name

var_name <- d$bike_children

d$var_name_f <- revalue(as.factor(var_name), c("1" = "Never", "2" = "Sometimes", "3" = "Often", "4" = "Always"))

var_name_f <- d$var_name_f

##### Table

t_1 <- d %>%
          group_by(wave_id, var_name_f) %>%
            summarise(n = n()) %>%
            mutate(pct = n / sum(n))

kable(t_1)  %>%   kable_styling(bootstrap_options = "striped", full_width = T, position = "left")

##### Figure

p <- ggplot(d, aes(var_name_f,  fill = var_name_f)) + theme(axis.text.x = element_text(angle=90, vjust = .6)) + 
  geom_bar() +
  scale_fill_manual(values = INTERACTPalette3) +
  guides(fill=FALSE) +
      ylab("Count") +
      xlab("Perception of bicycle risk") +
      ggtitle("How often are your cycling trips made with children?") + 
  facet_wrap(~ wave_id)
plot(p)
```

## Q5: Do you currently use any of the following roads when you bike in Victoria?{.tabset}

### Cook St or Fifth St

```{r, echo=FALSE}

var_name <- d$vicroads_a

d$var_name_f <- revalue(as.factor(var_name), c("1" = "Yes", "2" = "No", "77" = "Don't know"))

var_name_f <- d$var_name_f

##### Table

t_1 <- d %>%
          group_by(wave_id, var_name_f) %>%
            summarise(n = n()) %>%
            mutate(pct = n / sum(n))

kable(t_1)  %>%   kable_styling(bootstrap_options = "striped", full_width = T, position = "left")

##### Figure

p <- ggplot(d, aes(var_name_f,  fill = var_name_f)) + theme(axis.text.x = element_text(angle=90, vjust = .6)) + 
  geom_bar() +
  scale_fill_manual(values = INTERACTPalette3) +
  guides(fill=FALSE) +
      ylab("Count") +
      xlab("Cook Street or Fifth Street") +
      ggtitle("Do you currently use any of the following roads") + 
  facet_wrap(~ wave_id)
plot(p)
```

### Fairfield Rd or Humboldt St

```{r, echo=FALSE}

var_name <- d$vicroads_b

d$var_name_f <- revalue(as.factor(var_name), c("1" = "Yes", "2" = "No", "77" = "Don't know"))

var_name_f <- d$var_name_f

##### Table

t_1 <- d %>%
          group_by(wave_id, var_name_f) %>%
            summarise(n = n()) %>%
            mutate(pct = n / sum(n))

kable(t_1)  %>%   kable_styling(bootstrap_options = "striped", full_width = T, position = "left")

##### Figure

p <- ggplot(d, aes(var_name_f,  fill = var_name_f)) + theme(axis.text.x = element_text(angle=90, vjust = .6)) + 
  geom_bar() +
  scale_fill_manual(values = INTERACTPalette3) +
  guides(fill=FALSE) +
      ylab("Count") +
      xlab("Fairfield Road or Humboldt Street") +
      ggtitle("Do you currently use any of the following roads") + 
  facet_wrap(~ wave_id)
plot(p)
```

### Fort St

```{r, echo=FALSE}
var_name <- d$vicroads_c

d$var_name_f <- revalue(as.factor(var_name), c("1" = "Yes", "2" = "No", "77" = "Don't know"))

var_name_f <- d$var_name_f

##### Table

t_1 <- d %>%
          group_by(wave_id, var_name_f) %>%
            summarise(n = n()) %>%
            mutate(pct = n / sum(n))

kable(t_1)  %>%   kable_styling(bootstrap_options = "striped", full_width = T, position = "left")

##### Figure

p <- ggplot(d, aes(var_name_f,  fill = var_name_f)) + theme(axis.text.x = element_text(angle=90, vjust = .6)) + 
  geom_bar() +
  scale_fill_manual(values = INTERACTPalette3) +
  guides(fill=FALSE) +
      ylab("Count") +
      xlab("Fort Street") +
      ggtitle("Do you currently use any of the following roads") + 
  facet_wrap(~ wave_id)
plot(p)
```

### Government St

```{r, echo=FALSE}
var_name <- d$vicroads_d

d$var_name_f <- revalue(as.factor(var_name), c("1" = "Yes", "2" = "No", "77" = "Don't know"))

var_name_f <- d$var_name_f

##### Table

t_1 <- d %>%
          group_by(wave_id, var_name_f) %>%
            summarise(n = n()) %>%
            mutate(pct = n / sum(n))

kable(t_1)  %>%   kable_styling(bootstrap_options = "striped", full_width = T, position = "left")

##### Figure

p <- ggplot(d, aes(var_name_f,  fill = var_name_f)) + theme(axis.text.x = element_text(angle=90, vjust = .6)) + 
  geom_bar() +
  scale_fill_manual(values = INTERACTPalette3) +
  guides(fill=FALSE) +
      ylab("Count") +
      xlab("Government Street") +
      ggtitle("Do you currently use any of the following roads") + 
  facet_wrap(~ wave_id)
plot(p)
```

### Haultain St or Kings Rd

```{r, echo=FALSE}
var_name <- d$vicroads_e

d$var_name_f <- revalue(as.factor(var_name), c("1" = "Yes", "2" = "No", "77" = "Don't know"))

var_name_f <- d$var_name_f

##### Table

t_1 <- d %>%
          group_by(wave_id, var_name_f) %>%
            summarise(n = n()) %>%
            mutate(pct = n / sum(n))

kable(t_1)  %>%   kable_styling(bootstrap_options = "striped", full_width = T, position = "left")

##### Figure

p <- ggplot(d, aes(var_name_f,  fill = var_name_f)) + theme(axis.text.x = element_text(angle=90, vjust = .6)) + 
  geom_bar() +
  scale_fill_manual(values = INTERACTPalette3) +
  guides(fill=FALSE) +
      ylab("Count") +
      xlab("Haultain Street or Kings Road") +
      ggtitle("Do you currently use any of the following roads") + 
  facet_wrap(~ wave_id)
plot(p)
```

### Pandora Ave

```{r, echo=FALSE}
var_name <- d$vicroads_f

d$var_name_f <- revalue(as.factor(var_name), c("1" = "Yes", "2" = "No", "77" = "Don't know"))

var_name_f <- d$var_name_f

##### Table

t_1 <- d %>%
          group_by(wave_id, var_name_f) %>%
            summarise(n = n()) %>%
            mutate(pct = n / sum(n))

kable(t_1)  %>%   kable_styling(bootstrap_options = "striped", full_width = T, position = "left")

##### Figure

p <- ggplot(d, aes(var_name_f,  fill = var_name_f)) + theme(axis.text.x = element_text(angle=90, vjust = .6)) + 
  geom_bar() +
  scale_fill_manual(values = INTERACTPalette3) +
  guides(fill=FALSE) +
      ylab("Count") +
      xlab("Pandora Avenue") +
      ggtitle("Do you currently use any of the following roads") + 
  facet_wrap(~ wave_id)
plot(p)
```

### Shelbourne St or Begbie St

```{r, echo=FALSE}
var_name <- d$vicroads_g

d$var_name_f <- revalue(as.factor(var_name), c("1" = "Yes", "2" = "No", "77" = "Don't know"))

var_name_f <- d$var_name_f

##### Table

t_1 <- d %>%
          group_by(wave_id, var_name_f) %>%
            summarise(n = n()) %>%
            mutate(pct = n / sum(n))

kable(t_1)  %>%   kable_styling(bootstrap_options = "striped", full_width = T, position = "left")

##### Figure

p <- ggplot(d, aes(var_name_f,  fill = var_name_f)) + theme(axis.text.x = element_text(angle=90, vjust = .6)) + 
  geom_bar() +
  scale_fill_manual(values = INTERACTPalette3) +
  guides(fill=FALSE) +
      ylab("Count") +
      xlab("Shelbourne Street or Begbie Street") +
      ggtitle("Do you currently use any of the following roads") + 
  facet_wrap(~ wave_id)
plot(p)
```

### Harbour Rd, Wharf St or Belville St

```{r, echo=FALSE}
var_name <- d$vicroads_h

d$var_name_f <- revalue(as.factor(var_name), c("1" = "Yes", "2" = "No", "77" = "Don't know"))

var_name_f <- d$var_name_f

##### Table

t_1 <- d %>%
          group_by(wave_id, var_name_f) %>%
            summarise(n = n()) %>%
            mutate(pct = n / sum(n))

kable(t_1)  %>%   kable_styling(bootstrap_options = "striped", full_width = T, position = "left")

##### Figure

p <- ggplot(d, aes(var_name_f,  fill = var_name_f)) + theme(axis.text.x = element_text(angle=90, vjust = .6)) + 
  geom_bar() +
  scale_fill_manual(values = INTERACTPalette3) +
  guides(fill=FALSE) +
      ylab("Count") +
      xlab("Harbour Road, Wharf Street, or Belleville Street") +
      ggtitle("Do you currently use any of the following roads") + 
  facet_wrap(~ wave_id)
plot(p)
```

### Galloping Goose or the E&N Trail

```{r, echo=FALSE}
var_name <- d$vicroads_i

d$var_name_f <- revalue(as.factor(var_name), c("1" = "Yes", "2" = "No", "77" = "Don't know"))

var_name_f <- d$var_name_f

##### Table

t_1 <- d %>%
          group_by(wave_id, var_name_f) %>%
            summarise(n = n()) %>%
            mutate(pct = n / sum(n))

kable(t_1)  %>%   kable_styling(bootstrap_options = "striped", full_width = T, position = "left")

##### Figure

p <- ggplot(d, aes(var_name_f,  fill = var_name_f)) + theme(axis.text.x = element_text(angle=90, vjust = .6)) + 
  geom_bar() +
  scale_fill_manual(values = INTERACTPalette3) +
  guides(fill=FALSE) +
      ylab("Count") +
      xlab("Galloping Goose Trail or the E and N Trail") +
      ggtitle("Do you currently use any of the following roads") + 
  facet_wrap(~ wave_id)
plot(p)
```

## Q6: How much would you agree with the following statement: "I would like to travel by bicycle more than I do now"?

```{r, echo=FALSE}

var_name <- d$bike_more

d$var_name_f <- revalue(as.factor(var_name), c("1" = "Strongly Agree", "2" = "Somewhat Agree", "3" = "Somewhat Disagree", "4" = "Strongly Disagree", "77" = "Don't Know"))

var_name_f <- d$var_name_f

##### Table

t_1 <- d %>%
          group_by(wave_id, var_name_f) %>%
            summarise(n = n()) %>%
            mutate(pct = n / sum(n))

kable(t_1)  %>%   kable_styling(bootstrap_options = "striped", full_width = T, position = "left")

##### Figure

p <- ggplot(d, aes(var_name_f,  fill = var_name_f)) + theme(axis.text.x = element_text(angle=90, vjust = .6)) + 
  geom_bar() +
  scale_fill_manual(values = INTERACTPalette3) +
  guides(fill=FALSE) +
      ylab("Count") +
      xlab("I would like to travel by bicycle more than I do now") +
      ggtitle("How much would you agree with the following statement") + 
  facet_wrap(~ wave_id)
plot(p)
```


## Q7: How comfortable would you feel biking in the following places?

```{r, echo=FALSE}
var_name <- d$bike_comf_a

d$var_name_f <- revalue(as.factor(var_name), c("1" = "Very uncomfortable", "2" = "	Somewhat uncomfortable", "3" = "Somewhat comfortable", "4" = "Very comfortable", "77" = "Don't Know"))

var_name_f <- d$var_name_f

##### Table

t_1 <- d %>%
          group_by(wave_id, var_name_f) %>%
            summarise(n = n()) %>%
            mutate(pct = n / sum(n))

kable(t_1)  %>%   kable_styling(bootstrap_options = "striped", full_width = T, position = "left")

##### Figure

p <- ggplot(d, aes(var_name_f,  fill = var_name_f)) + theme(axis.text.x = element_text(angle=90, vjust = .6)) + 
  geom_bar() +
  scale_fill_manual(values = INTERACTPalette3) +
  guides(fill=FALSE) +
      ylab("Count") +
      xlab("A path or trail separate from the street?") +
      ggtitle("How comfortable would you feel biking in the following places") + 
  facet_wrap(~ wave_id)
plot(p)
```